---
title: "EDS241: Assignment 2"
author: "Jake Eisaguirre"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  - \setlength{\parindent}{1em}
  - \usepackage{float}
--- 
  
```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(here)
library(tidyverse)
library(janitor)
library(kableExtra)
library(estimatr)
library(broom)
library(readxl)
```

### Clean and plot data

\noindent The following code loads and cleans the data.
```{r}
data <- read_excel(here("NBP.xls")) %>% 
  clean_names()
```

### (a) Make a histogram depicting the distribution of Dnox_masstons

\noindent The following code plots the data
```{r}

ggplot(data = data, aes(x = dnox_masstons)) +
  geom_histogram() +
  theme_classic()

  
```

### (b) Create an indicator =1 if the county has PctBlack above the sample median, and =0 otherwise (in the rest of the assignment, I refer to this variable as ‘D’). What is the average of PctBlack for counties above the median, i.e. counties for which D=1?

\noindent The following code finds the median of PctBlack and creates an indicator of 1 if above the medium and finds the average of PctBlack for counties above the median
```{r}
med <- print(median(data$pct_black))

data <- data %>%
  mutate(D = ifelse(pct_black > med, c(1), c(0))) 

ave_pctblack <- data %>% 
  filter(D == 1) %>% 
  summarise(ave_pctBlack = mean(pct_black))

print(ave_pctblack)

kable(ave_pctblack)

```

\noindent The average PctBlack for counties above the median is 19.313.


### (c) Estimate a regression of Dnox_masstons on NBP. Interpret the estimated intercept and the coefficient on NBP.

\noindent The following code regresses Dnox_masstons on NBP
```{r}
mod1 <- lm_robust(dnox_masstons ~ nbp, data = data)

tidy(mod1) %>% 
  kable()
```
\noindent Intercept: On average when the county has not been regulated under the NOx Budget program (nbp = 0) the change in NOx emmisions from all power plants in the counties between 2000-2008 will be -3.62 tons. 

Slope: When the county has been regulated under the NOx Budget program (nbp = 1) the change in NOx emmissions from all power plants in the counties between 2000-2008 will be -3.92 tons.


### (d) Create an interaction between the variables NBP and D. Estimate a regression of Dnox_masstons on NBP, D, and this interaction. Interpret each estimated regression coefficient, including the intercept.

\noindent The following code regresses dnox_masstons on NBP, D (median indicator of pct_black), and NBP as an interaction with D.
```{r}
mod2 <- lm_robust(dnox_masstons ~ nbp + D + nbp:D, data = data)

tidy(mod2) %>% 
  kable()
```
\noindent NBP: When all else is held constant, on average counties that have been regulated under the NOx Budget program (nbp = 1) will have a change in NOx emmissions from all power plants in the counties between 2000-2008 of -7.14 tons when above the median compared to below the median.

D: When all else is held constant, on average counties that have an average PctBlack above the median (19.31)(D=1) will have a change in NOx emmissions from all power plants in the counties between 2000-2008 of -2.59 tons when above the median compared to below the median.

NBP:D : The impact of NOx Budget program on NOx emmissions from all power plants in the counties between 2000-2008 is 6.37 tons greater in communities that have an average PctBlack above the median (19.31)(D=1) then communities that have an average PctBlack below the median (19.909)(D=0).

Intercept: On average when the county has not been regulated under the NOx Budget program (nbp = 0) and the PctBlack is below the median (19.31)(D=0) the change in NOx emmisions from all power plants in the counties between 2000-2008 will be -2.42 tons


### (e) What is the predicted Dnox_masstons in a county that was not regulated under NBP and where PctBlack is above the sample median (i.e., where D=1)? Report the 95% confidence interval for this prediction. Make sure to use “heteroskedasticity-robust” standard errors.

\noindent The following code regresses dnox_masstons on counties not regulated by NBP and where the PctBlack is above the sample median (D=1)
```{r}

mod3 <- lm_robust(dnox_masstons ~ nbp + D , data = data)
pred_data <- data.frame(nbp=c(0), D=c(1))

tidy(mod3) %>% 
  kable()

predict(mod3, newdata = pred_data, se.fit = T, interval = 'confidence')

  
```
\noindent The predicted change in NOx emmissions from all power plants in the counties between 2000-2008 under no regulation from NBP (NBP=0) and when the PctBacl is below the sample median (D=0) is -3.52 tons. The 95% confidence under heterskedasticity-robust standard errors is -4.82 tons - -2.21 tons.
